Stochastic Gradient Descent

### 2018-03-21 sgd/sgd.tex
finished final presentation

	In \textbf{parametric} statistics, we often make assumptions that make this optimization ``nice'':
	\begin{itemize}
		\item \small Example: in OLS, we do not need to try
			different values
			of $\hat{\beta}$ to see which minimizes the loss
			function, we (typically) can just evaluate
			$(X'X)^{-1}X'Y$ \\~\\
	\end{itemize}
	\smallskip

@@

\begin{frame}
	\frametitle{Other times, optimization is not so easy}
	Suppose that we have a typical supervised classification problem:
	\begin{itemize}
		\item \small Non-parametric: no assumptions about distribution of data
		\item Feature vector $\mathbf{X}_i$, label $Y_i$
		\item Want to find best prediction function $f_w^*$ from class $\mathcal{F}$
		\item Optimization: pick weights $\bm{w}$ that minimize
			empirical risk according to some convex
			loss function $L(f_w(x), y)$ \\~\\
	\end{itemize}

@@

	Stop if $\mathbf{w}_t - \ldots \leq \epsilon$ \\~\\

>>>>

	In \textbf{parametric} statistics, we often make assumptions that make this optimization ``nice''
	\begin{itemize}
		\item \small Example: in OLS, we do not need to try
			different values
			of $\hat{\beta}$ to see which minimizes the loss
			function, we (typically) can just evaluate
			$(X'X)^{-1}X'Y$ \\~\\
	\end{itemize}
	\smallskip

@@

\begin{frame}
	\frametitle{Other times, optimization is not so easy}
	Suppose that we have a typical supervised classification problem
	\begin{itemize}
		\item \small Non-parametric: no assumptions about distribution of data
		\item Feature vector $\mathbf{X}_i$, label $Y_i$
		\item Want to find best prediction function $f_w^*$ from class $\mathcal{F}$
		\item Optimization: pick weights $\bm{w}$ that minimize
			empirical risk according to some convex
			loss function $L(f_w(x), y)$ \\~\\
	\end{itemize}

@@

	Stop if gradient $\leq \epsilon$ \\~\\
